Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-04-23 Tex/CAV2019/Trindade_Cordeiro_VSTTE2020.tex
Revised Section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
%---------------------------------------------------------------------------
\subsection{Description of the Case Studies}
%---------------------------------------------------------------------------
The proposed synthesis approach was evaluated in seven stand-alone PV system case studies.
These case studies were defined based on the usual electrical load found in riverside communities in the Amazonas State, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized to support a few lamps and a 12k BTUs air-conditioner solution. 
Here we report each case study as a 4-tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
\textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}. This 4-tuple represents the Algorithm~\ref{alg:opt-algorithm} inputs. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems. 
%
Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc file.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.

@@

In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank, in a comparison for a entire years weather data of simulation in order to guarantee that the proposed sizing meets the electrification requirements. PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation and data analysis of solar PV systems. It contains: design, sizing, 3D shading scene, simulation, grid and off-grid features. It uses world wide irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and ageing analysis~\cite{PVsyst2017}. However, it does not performs optimization. Drawbacks of PVsyst: it does nor perform optimization therefore it needs the system sized in order to validated it, PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for few seconds. PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.

%---------------------------------------------------------------------------
\subsection{Objectives and Setup}
%---------------------------------------------------------------------------
Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?; [EG2] \textbf{(performance)} How do the symbolic verifiers compare to each other for synthesizing PV systems?; and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10. The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favourable to HOMER Pro. PVsyst used the same configuration as HOMER Pro. We perform the experiments with a predefined time out of $660$ minutes.

@@

The violation (SAT result) indicated all over the Table~\ref{tab1} 
is the $assert$ of line $21$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.

@@

CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes. Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left size as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron  Energy, and the inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power. The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample as well, shows the number of panels and batteries and how they are connected.

Case studies $2$, $3$, $6$, and $7$  led to a \textit{time out} result in CPAchecker, i.e.  it was not solved within $660$ minutes.

\begin{figure}[h]
\fbox{\includegraphics[width=1.0\textwidth]{CPA_opt_c5.png}}
\centering
\caption{Counterexample generated by CPAchecker after validation of case 5 (file Counterexample.html).}
\label{fig:CPAoptc1}
\end{figure}

An internal failure was presented by ESBMC when using Z3 solver in all case studies. It corresponds to a 'bug' in the Z3 solver which will require an updated version of ESBMC to fix it. However, when using the incremental BMC configuration of ESBMC with Boolector solver, the verifier engine was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response varying from $36.70$ to $620$ minutes. Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated.  ESBMC with this configuration was not possible to obtain a optimal solution in cases $2$ and $7$. Case $2$ reached a  \textit{time out} result after $660$ minutes of processing. Moreover, case $7$ resulted in a UNSAT result, i.e the verifier engine was not possible to get a feasible solution considering the list of equipment. This SAT situation was reached after just $0.48$ minutes.

@@

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e. the tool always tries to feed the given load with electricity $365$ days/year.

Certain other HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller . HOMER Pro includes a controller automatically just to simulate the charge/discharge of batteries and to meet the load requirement; however, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing; (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with a $83.4$ Ah lead-acid battery and during simulation, HOMER Pro did not try to use other capacities or types; and (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e. it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.

The authors had four PV systems deployed and monitored since June $2018$ in a riverside community in State of Amazonas, Brazil, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, total of $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.

@@

Comparing the results of the formal synthesis with CPAchecker, and ESBMC, against those of  HOMER Pro, it was observed some distinct results, in terms of technical solution and cost (cf. Table~\ref{tab1}).  Related to performance there is a huge difference in favour of HOMER Pro that obtained the results in considerably less time: few seconds in opposite of an average of $234$ minutes for the automated synthesis technique.

Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always having a higher estimation from the automated synthesis technique. However, considering that the cost of individual item of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.

In one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool. The difference varied from $19$\% to $65$\%. In the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro. The difference was among $34$\% to $68$\%. The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.

Those discrepancies are not easy to address without some real systems validation. However we use the simulation software PVsyst in order to validate the optimal sizing produced. According PVsyst, we have to each case study:

\begin{itemize}
  	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise), therefore the sizing that was done "by hand" is not correct. Concerning our produced sizing, it was not found error during the 365-day of the year simulation, the same result for HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. This case has not field deployed to compare, and our approach did not produce solution. Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
	\item Case study 3: only our approach produced the optimal solution because there is the requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries. This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $87$\%. Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries. This one was deployed at the field, and PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries). Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 6: PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries. This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $85.65$\%. Concerning our optimal solution it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries. This case has not field deployed to compare, and our approach did not produce feasible solution with the equipment list available. Only HOMER Pro left to comparison, however PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
\end{itemize}

Each simulation with PVsyst took 4 seconds. Overall, those comparison between our approach and optimization tool, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.

%As a comparison, consider case study $5$: the optimal solution provided by HOMER Pro requires $17$\% more PV panels than the solution presented by the synthesis tool, and HOMER Pro does not show the arrangement of arrays (i.e. the number of series and parallel PV panels); the battery bank presented by HOMER Pro provides a capacity of $417$ Ah ($5 \times 83.4$ Ah), while the synthesis tool presented an optimal solution with a total capacity of $560$ Ah ($7 \times 80$ Ah) and this represent a difference of $34$\%.

HOMER Pro suggests a value in kW for the inverters that is very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed. The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst. This is a clear advantage of the formal synthesis method.

HOMER Pro does not include charge controllers as an explicit item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis. The formal synthesis method, therefore, presents more reliable results than HOMER Pro.

@@

Summarizing, our synthesis tool is capable of presenting a solution which is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer data sheet, including  the model of the component, nominal current and voltage. In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising). Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results.

>>>>

%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------
%---------------------------------------------------------------------------
\subsection{Description of the Case Studies}
%---------------------------------------------------------------------------

The proposed synthesis approach was evaluated in seven stand-alone PV system case studies.
These case studies were defined based on the usual electrical load found in riverside communities in the Amazonas State, Brazil~\cite{TrindadeCordeiro19,Agrener2013}, except for case 7, which was idealized to support a few lamps and a 12k BTUs air-conditioner solution. 
Here we report each case study as a 4-tuple \textit{\{power peak (W); power surge (W); energy consumption (Wh/day); battery autonomy (hours)\}} as follows:
\textbf{1:} \{342; 342; 3,900; 48\}; \textbf{2:} \{814; 980; 4,880; 48\}; \textbf{3:} \{815; 980; 4,880; 12\}; \textbf{4:} \{253; 722; 3,600; 48\}; \textbf{5:} \{263; 732; 2,500; 48\}; \textbf{6:} \{322; 896; 4,300; 48\}; \textbf{7:} \{1,586; 2,900; 14,000; 48\}. This 4-tuple represents the Algorithm~\ref{alg:opt-algorithm} inputs. For all cases, an estimated load curve (kWh) was defined based on the electronics consumers in each house. Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems. 
%
Three start-of-the-art verifiers, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 file.c -\phantom{}-trace} v5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc file.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} v6.0.0~\cite{esbmc2018} with the Boolector 3.0.1 solver~\cite{Brummayer}, and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc file.c} v1.8~\cite{Beyer2011} with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency.

@@

In order to validate and compare the optimal sizing solution produced by our approach and by HOMER Pro, we use a complete simulation tool, called PVsyst version $6.86$, with plenty of commercial equipment in its data bank. We have considered a comparison for an entire year's weather data of simulation to guarantee that the proposed sizing meets the electrification requirements. PVsyst is a PC software package developed by a Swiss company used globally for the study, sizing, simulation, and data analysis of solar PV systems. PVsyst contains: design, sizing, 3D shading scene, simulation, grid, and off-grid features. It uses comprehensive irradiation data from Meteonorm\footnote{https://meteonorm.com/en/}, and aging analysis~\cite{PVsyst2017}. However, it does not perform optimization. Drawbacks of PVsyst: it does not perform optimization; therefore, it needs the system sized in order to validate it. PVsyst does not have commercial inverter equipment and therefore does not consider surge power demand as the ones produced by air conditioners and refrigerators for a few seconds. PVsyst is a paid software with $30$-day test possibility and runs only in MS-Windows operational system.

%---------------------------------------------------------------------------
\subsection{Objectives and Setup}
%---------------------------------------------------------------------------

Our evaluation aims to answer three experimental goals: [EG1] \textbf{(soundness)} Does our automated synthesis approach provide correct results?; [EG2] \textbf{(performance)} How do the symbolic verifiers compare to each other for synthesizing PV systems?; and [EG3] \textbf{(state-of-the-art)} how does our formal synthesis tool compare to a specialized simulation tool?

All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB RAM, running Ubuntu $16.04$ LTS $64$-bits. For HOMER Pro, we have used an Intel Core i5-$4210$ ($4$-cores) with $1.7$ GHz and $4$ GB RAM running Windows 10. The hardware platform was not the same because of the availability of the machines; this has an impact on performance, which is less favorable to HOMER Pro. PVsyst used the same configuration as HOMER Pro. We perform the experiments with a predefined time out of $660$ minutes.

@@

The violation (SAT result) indicated all over the Table~\ref{tab1} 
is the $assert$ of the line $21$ from Algorithm~\ref{alg:opt-algorithm} and indicates that an optimal solution was found.

@@

CPAchecker was able to synthesize optimal sizing in three out of the seven case studies (cases $1$, $4$, and $5$): the result was produced within the time limit, which varied from $254.25$ to $548$ minutes. Fig.~\ref{fig:CPAoptc1} illustrates the result of case $5$ with the optimal sizing appearing on the left side as the integer $3$ for the solar panel (which is the Canadian CS6U-330P model of $330$ W from the manufacturer Victron Energy), battery $0$ refers to the model 12MF80 of $80$ Ah from Moura, charge controller $0$ refers to the model 35A-145V MPPT from Victron Energy. The inverter number $2$ refers to the Epever model IP350-11 of $280$ W (nominal power) and $750$ W of surge power. The variables NTP, NPS, NPP, NBS, NBP, and NBTotal, also presented in the counterexample, shows the number of panels and batteries and how they are connected.

Case studies $2$, $3$, $6$, and $7$ led to a \textit{time out} result in CPAchecker, i.e. it was not solved within $660$ minutes.  
%
\begin{figure}[h]
\fbox{\includegraphics[width=1.0\textwidth]{CPA_opt_c5.png}}
\centering
\caption{Counterexample generated by CPAchecker after validation of case 5 (file Counterexample.html).}
\label{fig:CPAoptc1}
\end{figure}

An internal failure was presented by ESBMC when using Z3 solver in all case studies. It corresponds to a 'bug' in the Z3 solver, which will require an updated version of ESBMC to fix it. However, when using the incremental BMC configuration of ESBMC with Boolector solver, the verifier engine was able to reach the optimal sizing of case studies $1$, $3$, $4$, $5$, and $6$ with a FAIL/ SAT response varying from $36.70$ to $620$ minutes. Fig.~\ref{fig:esbmcoptcase3} shows the counterexample generated. ESBMC with this configuration was not possible to obtain an optimal solution in cases $2$ and $7$. Case $2$ reached a \textit{time out} result after $660$ minutes of processing. Moreover, case $7$ resulted in a UNSAT result, i.e., the verifier engine was not possible to get a feasible solution considering the list of equipment. This SAT situation was reached after just $0.48$ minutes.

@@

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and in under $30$ seconds, much faster than the proposed automated synthesis tool (cf.~\textit{EG3}). Case study $3$ could not be simulated since HOMER Pro does not have the battery autonomy adjustment feature, i.e., the tool always tries to feed the given load with electricity $365$ days/year.

Certain other HOMER Pro drawbacks were also noted: (1) System equipment does not include an explicit charge controller. HOMER Pro includes a controller automatically to simulate the charge/discharge of batteries and to meet the load requirement. However, without costs or even with electrical characteristics such as maximum current and voltage, which are common during PV sizing. (2) HOMER Pro requires the inclusion of some battery specification to initiate optimization; however, it does not change the electrical specifications during simulation; the results presented are multiples of the original battery type suggested by the user. For example, it was started with a $83.4$ Ah lead-acid battery, and during simulation, HOMER Pro did not try to use other capacities or types. (3) HOMER Pro does not present the optimal solution in terms of connections of PV panel arrays, just the total in terms of power, i.e., it presents neither the models and the power of each PV panel nor the total of panels in series or parallel.

The authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the State of Amazonas, Brazil, with demands of case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S, a total of $975$ W) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries.

@@

Comparing the results of the formal synthesis with CPAchecker, and ESBMC, against those of HOMER Pro, it was observed some distinct results, in terms of technical solution and cost (cf. Table~\ref{tab1}). Concerning the performance, there exists a vast difference in favor of HOMER Pro that obtained the results in considerably less time: few seconds in the opposite of an average of $234$ minutes for the automated synthesis technique.

Particularly in the case of LCC, the cost varied from $11$\% to $44$\%, always having a higher estimation from the automated synthesis technique. However, considering that the cost of individual items of each database used to compose the optimal design is not the same among the tools, it is plausible to obtain distinct results.

On the one hand, related to the PV panels sizing, the results presented by the automated synthesis were smaller in terms of power than the produced by the simulation tool. The difference varied from $19$\% to $65$\%. On the other hand, related to the battery bank, the results were smaller in terms of capacity to the HOMER Pro. The difference was between $34$\% to $68$\%. The mathematical models are different and particular parameters can be tuned as well in each technique, and that can justify the difference, which was presented in all the case studies.

Those discrepancies are not easy to address without some real systems validation. However, we use the simulation software PVsyst in order to validate the optimal sizing produced. According to PVsyst, we have to each case study:

\begin{itemize}
 	\item Case study 1: PVsyst indicates that a minimum necessary of $1,166$ W of PV panels and $381$ Ah of batteries. This is a case that was deployed at the field ($975$ W of panels and $440$ Ah of batteries), and simulation showed that the availability is lower than the $95$\% ($91.06$\% to be precise); therefore the sizing that was done "by hand" is not correct. Concerning our produced sizing, it was not found error during the 365-day of the year simulation, the same result for HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.16$ times more for panels, and $1.31$ times more for batteries capability than necessary;
	\item Case study 2: PVsyst indicates that a minimum necessary of $1,482$ W of PV panels and $478$ Ah of batteries. This case has not field deployed to compare, and our approach did not produce a solution. Only HOMER Pro left to comparison. However, PVsyst showed that the sized PV system has $2.6$ times more panels and $1.74$ more batteries than the necessary;
	\item Case study 3: only our approach produced the optimal solution because there is a requirement of 12 hours of battery autonomy. HOMER Pro and PVsyst do not allow autonomy less than 24 hours;
	\item Case study 4: PVsyst indicates that a minimum necessary of $1,078$ W of PV panels and $354$ Ah of batteries. This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $87$\%. Concerning our optimal solution, it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 5: PVsyst indicates that a minimum necessary of $823$ W of PV panels and $268$ Ah of batteries. This one was deployed at the field, and PVsyst showed a correct sizing ($975$ W of panels and $440$ Ah of batteries). Concerning our optimal solution, it was not found error, the same as HOMER Pro. However the power values for panels and batteries show that HOMER Pro solution is oversized: $2.24$ times more for panels, and $1.41$ times more for batteries capability than necessary;
	\item Case study 6: PVsyst indicates that a minimum necessary of $1,299$ W of PV panels and $421$ Ah of batteries. This one was deployed at the field ($975$ W of panels and $440$ ah of batteries), and PVsyst showed a not correct sizing because the system availability was only $85.65$\%. Concerning our optimal solution, it was not found error, the same as HOMER Pro. However, the power values for panels and batteries show that HOMER Pro solution is oversized: $2.42$ times more for panels, and $1.38$ times more for batteries capability than necessary;
	\item Case study 7: PVsyst indicates that a minimum necessary of $4,263$ W of PV panels and $1,384$ Ah of batteries. This case has not field deployed to compare, and our approach did not produce a feasible solution with the equipment list available. Only HOMER Pro left to comparison. However, PVsyst showed that the sized PV system has $2.9$ times more panels and $1.99$ more batteries than the necessary.
\end{itemize}

Each simulation with PVsyst took 4 seconds. Overall, those comparisons between our approach and optimization tool, with validation through simulation tool, show that the synthesis solution is sound, which answers \textit{EG1 and EG3}.

HOMER Pro suggests a value in kW for the inverters that are very close to the maximum load of every case study, and it is just a reference value and not a commercial value of the inverter employed. The proposed synthesis tool, however, presents inverters that are commercial and can be bought off-the-shelf, moreover consider surge power demand from the house that is not considered by HOMER Pro or PVsyst. This is a definite advantage of the formal synthesis method.

HOMER Pro does not include charge controllers as a specific item of equipment in its mathematical model; only the synthesis tool presents a commercial controller and includes it during the cost analysis. The formal synthesis method, therefore, presents more reliable results than HOMER Pro.

@@

Summarizing, our synthesis tool is capable of presenting a solution that is far more detailed and closer to commercial conditions than the solution presented by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from the manufacturer datasheet, including the model of the component, nominal current, and voltage. In this respect, even the name of the manufacturer can be cited (in Table~\ref{tab1} it was removed to avoid unauthorized advertising). Moreover, the validation through PVsyst simulation, using the PV sizing produced by HOMER Pro and our synthesis approach, shows that our results are feasible and not as oversized as HOMER Pro results.
